\chapter{Introduction}
It is estimated that the human population will increase to nine billion people by 2050 \citep{Worldbank_2008}. This means that the food production needs to grow accordingly. With rice as the most important crop for regions with highest estimated population growth, rice will be the most important crop. \citet{Ray_2013_Yield} claimed that future rice production will need to grow by 2.4 percent per year in order to meet the demands of a growing population. However, pests and diseases are significant yield reducing factors in global rice production. \citet{Oerke_2005_Crop} estimated that rice pests potentially caused losses of nearly 37 percent of global rice production. To maintain food security, we need to increase yield productivity, and decrease yield losses. Addressing these yield-reducing factors is essential for food security not only in rice consuming societies, but also for other societies globally. 


Rice is predominantly grown in Asia, where thirty–one percent of global rice production comes from Southeast Asia alone \citep{OECD_2012_Agricultural}. The most intensive and productive areas are irrigated, where farmers can grow at least two rice crops per year. Approximately 45 percent of the rice growing area in Southeast Asia is irrigated, with the largest irrigated areas being found in Indonesia, Vietnam, Philippines, Thailand \citep{Mutert_2002_Developments}. In South Asia, the two major rice-growing countries are India and Bangladesh. India has the largest rice growing area globally, approximately 43 million hectares, and contributes 25 percent of global rice production alone. Combined, rice production in South and Southeast Asia contributes nearly half of global rice production. If rice production in South and Southeast Asia is threatened, it will significantly affect global rice production. 

Strategies of pest and disease management take sustainability, production efficiency, and environmental protection into account \citep{Mew_2004_Looking}. To achieve this, interactions between pests and human activities must be studied. A crop health survey may provide the necessary data which, together with adequate methods for analyzing this survey data, can produce preliminary information on their behaviors including major interactions \citep{Savary_1995_Use}. \citet{Savary_2000_Characterization} concluded that the observed injury profiles (\textit{i.e.}, the combination of disease and pest injury that may occur in a given farmer’s field) were strongly dependent on production situation. The authors discussed that pest management strategies should be developed according to the patterns of cropping practices, and a production situations. However, interactions among pests and environments under different locations or through time are difficult to elucidate, but are essential to design effective  strategies of pest management. 

To help visualize and understand these interactions, network analysis a promising tool for revealing the interactions among entities within a complex system. Network analysis have been applied in many scientific branches ranging from social sciences to computer sciences to biology \citep{Newman_2003_Structure}. A network model is an abstract model composed of a set of nodes or vertices and a set of edges, links or ties connected to the nodes. Nodes usually represent entities and the edges represent their relations. For example, an ecological network of a food web presents nodes as a species \citep{Krause_2003_Compartments} and edges as ecological relationships, or consider a social network of students (nods) in the school, where the edges are friendships \citep{Moody_2001_Race}.

In order to develop effective strategies of rice pest management, agronomists focus on holistic points related to crop health, but they do not focus on a particular aspects of plant protection. \citet{Savary_1995_Use,Savary_2000_Quantification} and \citet{Savary_2005_Multiple} discussed that (i) cropping practices strongly associate the pattern of disease syndromes and damage caused by animal pests, (ii) production situations are strongly related to the occurrence of individual disease, and (iii) production situations (a combination of physical and socioeconomic factors that influence agricultural production) represent very large risk factors (positive or negative) for the occurrences of disease syndromes.

These studies contributed to the body of knowledge needed to address crop health management. I have a good idea of which the relation of pests and diseases  affect and rice, production situation and their effect to rice yields, but we do not have a clear picture of where individual or groups of pests and diseases occur and how much effect they have on rice yield. One approach to gain more insight into the relationships of rice pests and disease in rice agroecosystems is to develop networks based on a wide range of pest and disease injuries and corresponding yield losses under different rice production situations across Asia. 


\subsection{Objectives of the study}

This study aimed to develop network approaches and apply them to analyze crop health survey data conducted in countries in South and Southeast Asia (India, Indonesia, Thailand, and Vietnam). 

Specifically, this research aims to:
\begin{enumerate}
\item ddevelop a network model based on crop health survey data and characterize relationships among rice injuries under rice agroecosystems in South and Southeast Asia, specifically in Tamil Nadu, and Odisha; India, West Java; Indonesia, Red rive delta; Vietnam, and central plain; Thailand;
\item compare the differential relationships of network models under different seasons and/or locations; and
\item apply network analysis to compare differential relationships of rice injuries in the network model under successive levels (low, medium and high) of crop cut data from different farmers' fields in South and Southeast Asia.
\end{enumerate}

\subsection{Significance of the study}

This research will be a significant contribution to rice pest management and will be an innovative approach to study rice crop health survey data. By understanding the relationships of cropping practices and rice injury profiles, over different locations on an international level, this study will be beneficial to the extentionists, agronomists and researchers for employing effective pest control management. Once network models based on crop health survey data are constructed, they will be beneficial to plant health authorities and the people who related to crop protection especially for rice. The network will support them to design specific strategies for rice pest and disease management and to limit the impact of these yield reducing factors. 

Moreover, the resulting network model will reveal the relationships between farmer’s practices (cropping practices) with the relationships of co-occurrence patterns of rice pest injuries. The approaches help us to understand the characteristics of  rice pests and diseases, which will provide the recommendations on how to design rice pest management. Importantly, it also serves as a new approach for researchers on the subjects of crop losses and epidemiology. 

\subsection{Scope and limitation of the study}

I determine co-occurrence relationships of rice injuries caused by animal pests and diseases. Data were from  surveys at the farmer's rice fields in South and Southeast Asia at differnt production environments (Central Plain; Thailand, Odisha; India, Red Rive Delta; Vietnam, Tamil Nadu; India, and West java; Indonesia) from 2013 to 2016. The survey data were conducted by following ``survey portfolio'' \citep{Savary_2009_Survey}.
