\section{Evaluation of correlation methods for co-occurrence network construction of rice crop health survey data}
\subsection{Introduction}

Pests are the blocks in the big wall of yield losses that plant protection specialists must scale due to the need to increase crop productivity. Surveys of farmers’ fields are useful sources of data to help us determine the importance of pests and understand complex relationships within agroecosystems. Network analysis is a promising tool frequently used to describe the pairwise relationships of a large number of variables. Network analysis of pest and disease incidence co-occurrence patterns offers new insight into pest management. Since different correlation measures lead to structurally different co-occurrence network and provide different information, selecting the optimal correlation method is critical. 

\subsection{Material and methods}
Survey data collected in 420 farmers’ fields in irrigated lowland rice growing areas in five Asian countries (India, Indonesia, Philippines, Thailand and Vietnam) were based on the “Survey Portfolio” . In this study, we evaluated correlation measures including, Pearson, Spearman, Kendal and Biweight mid correlation to discovering the true functionally related variables in crop health survey data.
Network models were visualized from correlation matrix with “igraph” package for R. 

\subsection{Result}
Evaluation of four correlation measures, including Pearson, Spearman, Kendall correlation, and Biweight mid-correlation shows two groups clustered according to hierarchical clustering using Euclidean distance. The Spearman and Kendall correlation were grouped in rank-base methods, and another group is non-rank-based correlations including Pearson correlation and Biweight mid-correlation. When choosing a measure, Spearman correlation was selected because its robustness to noise and to outliers.
Briefly, network analysis revealed that brown spot is the highest connection. Bacterial leaf streak, brown spot, white-backed planthopper, and brown planthopper have high node of connectivity

\subsection{Discussion}
The appropriate correlation measures for studied data should closely associate to the prior knowledge of biological correlation (2). For this study, nonlinear relationship between the abundances of brown plant hopper and white backed plant hopper was detected by a Spearman correlation but not by a Pearson correlation.
