\subsection{Materials and Methods}

\subsubsection{Study sites, data collection}

We survey the farmers' fields in five different production environments, which are Tamil Nadu  and Kerala, India; West Java, Indonesia; Laguna, Philippines; Central Plain, Thailand; and Mekong river delta, Vietnam for consecutive (2009 - 2013). These survey sites are in the major irrigated lowland rice growing areas, where rice is intensively cropped at least two seasons per year. The survey was conducted in both the rainy and dry seasons of 2010 to 2012 in India, Indonesia, Thailand, and Vietnam, except Philippines, which the survey was conducted in 2011. A total of 412 individual fields were surveyed in the five sites. The number of survey were summerize in Table \ref{table:Survey_data}. Each survey was regarded to be the representatives with a characteristic set of attributes, which were related to cropping practices, and environments.


The survey procedure and data were based on a standardized protocol described in ``A survey portfolio to characterize yield-reducing factors in rice'' developed by \citet{Savary_2009_Survey}. Rice injuries were collected in this study including the injuries caused by animal pests, pathogens, and weeds, which are harmful to rice plants, and importantly considered to reduce yield productivity. They were evaluated at booting and ripening stage according to survey procedure. Injuries on leaves such as whorl maggot injury (WM), leaffolder injury (LF), bacterial leaf blight (BLB), bacterial leaf streak (BLS), leaf blast (LB), brown spot (BS) were determined as a proportion of injured leaves. Injuries on tillers or hills such as stem rot (SR), sheath rot (SHR), sheath blight (SHB), whitehead (WH), deadheart (DH), Silver shoot (SS) were determined as a proportion of injured tillers or panicles. Weed infestation was determined as the percent of area are covered by any weed species above the rice canopy (WA) and the weed below the rice canopy (WB). Insect pests including brown planthopper (BPH), white backed planthopper (WPH), Green leafhopper (GLH), Rice bug or Stink bug (STB) were determined as number of insect found on the rice hill. 

Before analysis, data were compacted over time during crop growth. Two types of data were computed, depending on the nature of injury \citet{Savary_2009_Survey}. One is an area under injury progress curve (AUIPC) used for injury variables, which present on the leaves, and for weed infestation. Another is the maximum level at any of the two observations used for injury variables that can be observed on tillers, panicles, and hills, and insect pest count. The area under injury progress curve (AUIPC) \citep{Campbell_1990_Introduction} were calculated by the mid-point method using the following equation: The area under injury progress curve (AUIPC) was calculated by the midpoint method using the following equation::

\begin{equation}
AUIPC = \sum{\frac{1}{2(X_{i} + X_{i-1})(T_{i} - T_{i-1})}}
\end{equation}

where $X_i$ is percentage (\%) of leaves, tillers or panicles injured due to rice pests (e.g., leaf blast, leaf folder), or number of insects (e.g., plant hoppers, leaf hoppers) per quadrat, or percentage (\%) of weed infestation (ground coverage) at the $i$th observation, $T_i$ is time in rice development stage units (dsu) on a 0 to 100 scale (10: seedling, 20: tillering, 30: stem elongation, 40: booting, 50: heading, 60: flowering, 70: milk, 80: dough, 90: ripening, 100: fully mature) at the $i$th observation and $n$ is total number of observations.

\subsubsection{Network construction}

The co-occurrence network was inferred based on the Spearman correlation matrix constructed with \texttt{R} function \texttt{cor.test} with parameter method `Spearman' (package stats) was used for calculate Spearman's correlation coefficient ($\rho$), which is defined as the Pearson correlation coefficient between the ranked variables \cite{R_2015}. The nodes in this network represent injuries and the edges that connect these nodes represent correlations between injuries. Based on correlation coefficients and $P$-values for correlation, we constructed co-occurrence networks.The cutoff of $P$-values was 0.05. Network properties were calculated with the igraph package \citep{Csardi_2010_igraph}. All farmers' fields were divided into groups by country and season. The impact of each sample group on the Spearman correlation value of each edge in the network was assessed by Spearman correlation value of these fields. The network of each of group was detected the community structure by Walktrap algorithm by using \texttt{cluster\_walktrap} function of \textbf{igraph} package.


\subsubsection{Topological feature analysis}

We calculated two type of the topological features for each network level and node level in the network with the \textit{igraph} package. The node level feature set included betweenness (the number of shortest paths going through a node), closeness centrality (the number of steps required to access all other nodes from a given node), clsutering coefiicient (the probability that the adjacent nodes of a node are connected and degree (the number of adjacent edges). The betweenness centrality feature was used to measure the centrality of each node in the network.
Network level features: clustering diameter

 Nodes were further identified the key factors in the network. The way to identify key factors is to compare relative values of centrality such as eigenvector centrality and betweenness \cite{Valente_2008_How}. The residual of linear relationship between eigenvector centrality and betweeness and regress betweeness on eigenvector centrality can used as an indicators of key factors. A node with higher levels of betweenness and lower eigenvector centrality can be inferred as a central of the functioning of the network. Nodes with lower levels of betweenness and higher eigenvector centrality mare recognized as a key to the functioning of the network. 


We calculated the following topology metrics for each network: clustering coefficient, average node connectivity, diameter of the network, and average path length between nodes (species) of each network. The clustering coefficient measures the degree to which nodes of the network tend to cluster together and is a measure of the connectedness of the network and is indicative of the degree of species linkage in the network (Newman 2003). Node connectivity is a measure of the number of nodes that need to be removed to disconnect the remaining nodes from each other and is a measure of network robustness (Diestel 2005). In an ecological context, this node connectivity can also be inferred to be a measure of stability of interactions. Average path length is the average number of steps along the shortest paths for all possible pairs of network nodes, and diameter is the greatest distance between any pair of nodes. In our analysis, both diameter and average path length are considered measures of the size of the network. Larger networks are less connected, meaning that the likelihood of a strong connection between any two randomly selected species is low.

The network attributes (average path length, diameter, and cluster coefficient) for the temporal and spatial co-oc- currence networks were compared across systems using one- way ANOVA





