Rice injuries were included the injuries caused by animal pests, diseases, and also weed infestation, which are harmful to rice plants, and importantly considered to reduce yield productivity. They were grouped in the field assessment procedure according to their mechanisms. Injuries on leaves such as bacterial leaf blight (BLB), bacterial leaf streak (BLS), leaf blast (LB), brown spot (BS) were determined as a proportion of injured leaves. Injuries on tillers or hills such as stem rot, sheath rot, sheath blight, whitehead, dead-heat were determined as a proportion of injured tillers  or panicles.  Weed infestration were determined as the percent of weed above the rice canopy (WA) and the weed below the rice canopy (WB). 

# i am not sure that i will include the brown plant hoppper  in to the analysis (PH: number of insects sampled




also simplified. Although a very large number of pathogens, insects, and weeds are harmful to rice, many are seldom considered to cause yield losses. Diseases such as narrow brown spot, bacterial leaf streak, leaf scald, and leaf smut, and insects such as rice bugs, rice hispa, and defoliators in general are not considered to represent major, widespread, yield-reducing factors.  A second aspect pertains to the injury mechanisms, and Table 1 includes injuries that were grouped in the field assessment procedure according to their nature: photosynthetic area stealers (BLB, BS, LB: proportion of injured leaves), senescence accelerators (BLB, SHB, LB: proportion of injured leaves, except for SHB), tissue users (leaves: RWM, LF: proportion of injured leaves; tillers: SR, SHB, DH: proportion of injured tillers; panicles: SHR, WH: proportion of injured panicles), assimilate sappers (PH: number of insects sampled), turgor reducers (at the tiller level: SR, SHB: proportion of injured tillers; at the panicle level: NB: proportion of injured panicles), and stand reducers (WA and WB).